Results

### 2021-08-18 Analysis/03_Summarise_results.Rmd
updated fancy names

```{r, echo = FALSE}
rownames(model_table) <- gsub("\n", "_", fancy_names)
kable(model_table, caption = "Results of the model scaled metric ~ removal level per stressor", align = "c")
```

```{r, echo = FALSE}
rownames(null_table) <- fancy_names
## Even fancier column names
colnames(null_table) <- gsub(".d_rm", ".rm", colnames(null_table))
colnames(null_table) <- gsub("equalizing", "equa", colnames(null_table))
colnames(null_table) <- gsub("facilitation", "faci", colnames(null_table))
colnames(null_table) <- gsub("filtering", "filt", colnames(null_table))
colnames(null_table) <- gsub("competition", "comp", colnames(null_table))
kable(null_table, caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor", align = "c")
```

@@

## Get the right removal level
get.matrix.level <- function(results, level = 1) {
    do.call(cbind, lapply(results, function(X, level) return(X[, level, drop = FALSE]), level = level))
}
## Wrapper for pairs.panels (with fancy names)
pairs.panels.wrapper <- function(results, ...) {
    ## Make fancy names
    colnames(results) <- fancy.names(colnames(results), sep = ":\n")
    psych::pairs.panels(results, ...)
}

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$equalizing, level = 1))
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$equalizing, level = 2))
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$equalizing, level = 3))
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$equalizing, level = 4))
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$facilitation, level = 1))
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$facilitation, level = 2))
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$facilitation, level = 3))
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$facilitation, level = 4))
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$filtering, level = 1))
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$filtering, level = 2))
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$filtering, level = 3))
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$filtering, level = 4))
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$competition, level = 1))
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$competition, level = 2))
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$competition, level = 3))
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$competition, level = 4))
```

>>>>

```{r, echo = FALSE}
rownames(model_table) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
kable(model_table, caption = "Results of the model scaled metric ~ removal level per stressor", align = "c")
```

```{r, echo = FALSE}
rownames(null_table) <- gsub("\\]", "_", gsub("\\[", "_", gsub("\n", "", fancy_names)))
## Even fancier column names
colnames(null_table) <- gsub(".d_rm", ".rm", colnames(null_table))
colnames(null_table) <- gsub("equalizing", "equa", colnames(null_table))
colnames(null_table) <- gsub("facilitation", "faci", colnames(null_table))
colnames(null_table) <- gsub("filtering", "filt", colnames(null_table))
colnames(null_table) <- gsub("competition", "comp", colnames(null_table))
kable(null_table, caption = "Average difference between the null metric and the stressed metric (raw) for each level of removal and each stressor", align = "c")
```

@@

## Get the right removal level
get.matrix.level <- function(results, level = 1) {
    do.call(cbind, lapply(results, function(X, level) return(X[, level, drop = FALSE]), level = level))
}
## Wrapper for pairs.panels (with fancy names)
pairs.panels.wrapper <- function(results, metric.names, ...) {
    ## Make fancy names
    if(missing(metric.names)) {
        colnames(results) <- fancy.names(colnames(results), sep = ":\n")
    } else {
        colnames(results) <- metric.names
    }
    psych::pairs.panels(results, ...)
}

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$equalizing, level = 1), metric.names = fancy_names)
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$equalizing, level = 2), metric.names = fancy_names)
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$equalizing, level = 3), metric.names = fancy_names)
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$equalizing, level = 4), metric.names = fancy_names)
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$facilitation, level = 1), metric.names = fancy_names)
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$facilitation, level = 2), metric.names = fancy_names)
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$facilitation, level = 3), metric.names = fancy_names)
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$facilitation, level = 4), metric.names = fancy_names)
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$filtering, level = 1), metric.names = fancy_names)
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$filtering, level = 2), metric.names = fancy_names)
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$filtering, level = 3), metric.names = fancy_names)
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$filtering, level = 4), metric.names = fancy_names)
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$competition, level = 1), metric.names = fancy_names)
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$competition, level = 2), metric.names = fancy_names)
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$competition, level = 3), metric.names = fancy_names)
```

@@

```{r, fig.height = 18, fig.width = 18, echo = FALSE, eval = TRUE}
## Equalizing level 1
pairs.panels.wrapper(get.matrix.level(splitted_results$competition, level = 4), metric.names = fancy_names)
```
